Monte Carlo calculation to characterize neutron and gamma fields for ANITA neutron facility at TSL

### 2015-04-16 Paper2015.tex
Completed first draft of the gamma results subsection.

>>>>

Fig.~\ref{fig:GammaSpatialDistribution} shows the calculated spatial distribution of gamma photons at SUP and CUP.
Fig.~\ref{fig:DifferentialGammaSpectra} shows the calculated differential gamma spectra within the central region of the spatial distribution.
The results show\ldots\todo{Describe the gamma results}

\begin{figure}
    \centering
    \vspace{2in}
    \subfloat[SUP]{
        \hspace{\columnwidth}\todo{Add gamma spatial distribution at SUP, \SI{10.2}{\cm} collimator}
        \label{fig:GammaSpatialDistributionSUP}
    }\\
    \subfloat[CUP]{
        \hspace{\columnwidth}\todo{Add gamma spatial distribution at CUP, \SI{10.2}{\cm} collimator}
        \label{fig:GammaSpatialDistributionCUP}
    }
    \caption{Gamma spatial distribution}
    \todo{It would be better if gamma spatial distribution were expressed as dose, rather than number of photons. Not in time for the abstract submission, however!}
    \label{fig:GammaSpatialDistribution}
\end{figure}

\begin{figure}
    \centering
    \vspace{2in}
    \hspace{\columnwidth}
    \caption{Calculated differential gamma spectra at CUP and SUP}
    \label{fig:DifferentialGammaSpectra}
\end{figure}

Fig.~\ref{fig:GammaDoseEnergy} shows the calculated distribution of gamma dose, obtained by folding the gamma spectra (Fig~\ref{fig:GammaDoseEnergy}) with dose conversion data from \cite{tbd}.
The results show\ldots\todo{Describe the gamma dose versus energy graphs.}
The calculated dose rate at \SI{200}{\nA} primary proton current is \SI{21}{\milli\gray\per\hour} at SUP and \SI{370}{\milli\gray\per\hour} at CUP.\todo{Discuss calculated dose rates}

\begin{figure}
    \centering
    \vspace{2in}
    \subfloat[SUP]{
        \hspace{\columnwidth}\todo{Add gamma dose versus energy at SUP, \SI{10.2}{\cm} collimator}
        \label{fig:GammaDoseEnergySUP}
    }\\
    \subfloat[CUP]{
        \hspace{\columnwidth}\todo{Add gamma dose versus energy at CUP, \SI{10.2}{\cm} collimator}
        \label{fig:GammaDoseEnergyCUP}
    }
    \caption{Gamma dose spectra}
    \label{fig:GammaDoseEnergy}
\end{figure}
